---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vicdairymap

<!-- badges: start -->
<!-- badges: end -->

vicdairymap is a simple package containing sf objects for the Victorian dairy regions

Victoria has three  - Western, Gippsland and Murray - made up of are groups of local government areas. 

We have used this simple aggregation approach to create sf objects by summarising objects obtained using `strayr::read_absmap("lga2021")`

Local government areas outside of the non-dairy regions are assigned to arbirtary groups

## Installation

You can install the development version of vicdairymap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/vicdairymap")
```

## region_map

The following plot shows a map of the four regions which are contained in `vicdairymap::area_map`.

```{r region_map}
library(vicdairymap)

## basic region_map
ggplot2::ggplot(
  dairy_region_map,
  ggplot2::aes(
    geometry = geometry,
    fill = region_name,
    label = region_name,
    x = cent_long,
    y = cent_lat
    )
  ) +
  ggplot2::geom_sf(
   colour = "darkgrey"
   )+
  ggplot2::geom_label(
    data = dairy_region_map |> filter(is_dairy),
    colour = "black", fill = "grey", size = 3)+
  ggplot2::scale_fill_viridis_d(guide = "none")+
  ggthemes::theme_map()+
  ggplot2::theme(
    legend.position.inside = c(.7,.7)
  )

```





## region_tbl

The package contains a third dataset `vicdairymap::region_tbl` which shows the mapping of local government areas to regions.

```{r region_tbl}
## print full table of regions, areas and lgas
knitr::kable(
  dairy_region_tbl
)

```
