---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vicdairymap

<!-- badges: start -->
<!-- badges: end -->

vicdairymap is a simple package containing sf objects for the Victorian dairy regions

Victoria has three  - Western, Gippsland and Murray - made up of are groups of local government areas. 

We have used this simple aggregation approach to create sf objects by summarising objects obtained using `strayr::read_absmap("lga2021")`

Local government areas outside of the non-dairy regions are assigned to a 'Rest of Victoria' region.

## Installation

You can install the development version of vicdairymap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/vicdairymap")
```

## region_map

The following plot shows a map of the four regions which are contained in `vicdairymap::dairy_region_map`.

The three dairy regions are labelled.


```{r map}
library(vicdairymap)
library(sf)
## basic region_map
ggplot2::ggplot() +
  ggplot2::geom_sf(
    data = vicdairymap::dairy_region_map,
    ggplot2::aes(
      geometry = geometry,
      fill = region_name,
    ),  
   colour = "darkgrey"
   )+
  ggplot2::geom_label(
    data = 
      vicdairymap::dairy_region_map, 
    ggplot2::aes(
      label = region_name,
      x = cent_long,
      y = cent_lat
    ),
    colour = "black", fill = "grey", size = 3) +
  ggplot2::scale_fill_viridis_d(guide = "none") +
  ggthemes::theme_map() +
  ggplot2::theme(
    legend.position.inside = c(.7,.7)
  )

```





## region_tbl

The package contains a third dataset `vicdairymap::region_tbl` which shows the mapping of local government areas to regions.

```{r tbl}
## print full table of regions, areas and lgas
knitr::kable(
  dairy_region_tbl
)

```
